Report on Certificate Tools

### 2016-08-24 TEX/draft.tex
I tried to section the overview part, tommorow i will add text + finish OpenSSL text

\documentclass{report}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}
\usepackage{adjustbox,lipsum}

@@

\section{General}
\begin{table}[]
\centering
\caption{Overwiew General}
\label{my-label}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
                        & \multicolumn{3}{c|}{General}                   \\ \cline{2-4} 
\multirow{-2}{*}{Tools} & Type   & View + info                 & License \\ \hline
OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
Keygen                  & JKS    &                             &         \\ \hline
\end{tabular}
\end{center}
\end{table}

\section{Generation and signing of certificates}
\begin{table}[]
\centering
\caption{Generation and signing table}
\label{my-label}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
                        & \multicolumn{11}{c|}{Generation and signing}                                                                                                                                                                                                                                                                                                                                                                                                                                      \\ \cline{2-12} 
                        & \multicolumn{4}{c|}{Generate keys}                                                                                                                             &                               &                                          &                                                & \multicolumn{2}{c|}{Basic Constraints}                    &                                            &                                                                             \\ \cline{2-5} \cline{9-10}
\multirow{-3}{*}{Tools} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & Specify Type                & Specify path length         & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
OpenSSL                 & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
Keygen                  &                                                                      &                             &                             &                             &                               &                                          &                                                &                             &                             &                                            &                                                                             \\ \hline
                        &                                                                      &                             &                             &                             &                               &                                          &                                                &                             &                             &                                            &                                                                             \\ \hline
\end{tabular}
\end{center}
\end{table}

>>>>

\documentclass[10pt, a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}
\usepackage{adjustbox,lipsum}

\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{0cm}
\setlength{\textwidth}{500pt}

@@

\section{General}
%TABLE START
\begin{table}[h!]
\centering
\caption{Overwiew General}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|}
\hline
                        & \multicolumn{3}{c|}{General}                   \\ \cline{2-4} 
\multirow{-2}{*}{Tools} & Type   & View and information        & License \\ \hline
OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes & Public  \\ \hline
Keygen                  & JKS    &                             &         \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

\subsection{Type}
Sample text for defining what Type means

\subsection{View and information}
Sample text for definition.

\subsection{License}
Sample text for definition.

\section{Generation and signing of certificates}

\subsection{Keys, certificates and basic constraints}
%TABLE START
\begin{table}[h!]
\centering
\caption{Generation of keys and certificates and basic constrints}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
                       & \multicolumn{4}{c|}{Generate keys}                                                                                                                             & \multicolumn{2}{c|}{Basic Constraints}                    \\ \cline{2-7} 
\multirow{-2}{*}{Tool} & \begin{tabular}[c]{@{}c@{}}+\\  self-signed certificate\end{tabular} & + CSR                       & Specify length              & Specify algorithm           & Specify Type                & Specify path length         \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes                                          & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{34FF34}Yes \\ \hline
Keygen                 &                                                                      &                             &                             &                             &                             &                             \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

\subsubsection{Generate keys}

\paragraph{Self-signed certificate}
Some sample text.

\paragraph{Certificate Signing Request}
More sample text.

\paragraph{Specify length}
Even more sample text.

\paragraph{Specify algorithm}
You guessed it! More sample text.

\subsubsection{Basic Constraints}

\paragraph{Specify Type}
Not even trying to come up with sample text.

\paragraph{Specify path length}
Path length is long as long you wish it.

\subsection{Specifications}

%TABLE START
\begin{table}[h!]
\centering
\caption{Specifications}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                       &                               &                                          &                                                &                                            &                                                                             \\
\multirow{-2}{*}{Tool} & \multirow{-2}{*}{CSR signing} & \multirow{-2}{*}{Privkey + signed chain} & \multirow{-2}{*}{Specify certificate validity} & \multirow{-2}{*}{SAN for end certificates} & \multirow{-2}{*}{\begin{tabular}[c]{@{}c@{}}Support for\\ CSP\end{tabular}} \\ \hline
OpenSSL                & \cellcolor[HTML]{34FF34}Yes   & \cellcolor[HTML]{34FF34}Yes              & \cellcolor[HTML]{34FF34}Yes                    & \cellcolor[HTML]{34FF34}Yes                & \cellcolor[HTML]{34FF34}Yes                                                 \\ \hline
Keygen                 &                               &                                          &                                                &                                            &                                                                             \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

\paragraph{Certificate Signing Request signing}
Some random text.

\paragraph{Create combination of private key and signed chain}
Some random text.

\paragraph{Specify certificate validity}
Some random text.

\paragraph{Setting Subject Alternative Name for end certificates}
Some random text.

\paragraph{Support for Cryptographic Service Provider}
Some random text.

\section{Conversions}

%TABLE START
\begin{table}[h!]
\centering
\caption{Conversions}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{2}{c|}{Exporting}                                 &                                         &                                                                  \\ \cline{2-3}
\multirow{-2}{*}{Tools} & Certificate/chain only from file & Private key only            & \multirow{-2}{*}{Direct JKS and PKCS12} & \multirow{-2}{*}{Import certificate and private key into a file} \\ \hline
OpenSSL                 & \cellcolor[HTML]{34FF34}Yes      & \cellcolor[HTML]{34FF34}Yes & \cellcolor[HTML]{FF3A3A}No              & \cellcolor[HTML]{34FF34}Yes                                      \\ \hline
Keygen                  &                                  &                             &                                         &                                                                  \\ \hline
                        &                                  &                             &                                         &                                                                  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

\subsection{Exporting}

\subsubsection{Certificate or certificate chain from a file}
Some random text.

\subsubsection{Private key only}
Some random text.

\subsection{Direct conversion between Java Keystore and PKCS\#12 file}
Some random text.

\subsection{Importing of certificates and keys into storage files}
Some random text.
